Fusion Moves for Correlation Clustering

### 2014-11-12 paper/egpaper_for_review.tex
section title change
remove https

\noindent \textbf{Randomized Watersheds (RWS):}
%\subsubsection{Randomized Watersheds (RWS)}
Watersheds have become quite popular for
graph segmentation and have a strong connection
to energy minimization~\cite{couprie_2011}.
%
The edge weighted watershed algorithm~\cite{meyer_2013}
with random seeds can be used to get
cheap proposals.
To improve \emph{quality} we do not use $n$ seeds distributed uniformly
over all nodes but use the following.
%
We draw $n/2$ negative edges, and assign to the endpoints a different seed.
Doing so, a random subset of negative edges is forced
to be cut within each proposal.
For additional \emph{diversity}, noise $\mathcal{N} (0, sigma_{ws})$
can be added to the edge weighs.

@@

For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}\small{{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}}
of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.
For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use an modified version of
 the public available implementation in OpenGM\footref{opengm-master} of Kappes~\etal, as described in Sec.~\ref{sec:tunedMC}.
%
%We realize that their implementation has some limitations on large problems and make the following modifications.
%Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
%Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
%during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
%This procedure is one magnitude faster, but might cause a few extra outer iterations.
%In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
%For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
%
From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.

@@

\subsection{Tuned Multicut Algorithm}\label{sec:tunedMC} 
 \begin{figure}[t]
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[  mark size=1pt,
     height= 4cm, 
    restrict y to domain=-80000:1000,
   %   restrict x to domain=10:4000,
    xlabel = {runtime},
    xmin = 10,
    xmax = 4100,
    ymax = 0,
    ymin = -80000,
    legend to name = ledgendPositionMC,
    legend columns=4,
    width = 0.9\columnwidth,
    scaled ticks = false
    ] 
    \addplot[color=red,mark=x] table[x=time, y=MC-CCFDB-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-old}
    \addplot[color=orange,mark=o] table[x=time, y=MC-CCFDB-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-new}
    \addplot[color=blue,mark=x] table[x=time, y=MC-CCIFD-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-old}
    \addplot[color=cyan,mark=o] table[x=time, y=MC-CCIFD-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-new}

>>>>

\noindent \textbf{Randomized Watersheds (RWS):}
%\subsubsection{Randomized Watersheds (RWS)}
Watersheds have become quite popular for
graph segmentation and have a strong connection
to energy minimization~\cite{couprie_2011}.
%
The edge weighted watershed algorithm~\cite{meyer_2013}
with random seeds can be used to get
cheap proposals.
To improve \emph{quality} we do not use $n$ seeds distributed uniformly
over all nodes but use the following.
%
We draw $n/2$ negative edges, and assign to the endpoints a different seed.
Doing so, a random subset of negative edges is forced
to be cut within each proposal.
For additional \emph{diversity}, noise $\mathcal{N} (0, \sigma_{ws})$
can be added to the edge weighs.

@@

For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}}
of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use an modified version of
 the public available implementation in OpenGM\footref{opengm-master} of Kappes~\etal, as described in Sec.~\ref{sec:tunedMC}.
%
%We realize that their implementation has some limitations on large problems and make the following modifications.
%Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
%Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
%during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
%This procedure is one magnitude faster, but might cause a few extra outer iterations.
%In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
%For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
%
From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.

@@

\subsection{Improvements for the Multicut Algorithm}\label{sec:tunedMC} 
 \begin{figure}[t]
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[  mark size=1pt,
     height= 4cm, 
    restrict y to domain=-80000:1000,
   %   restrict x to domain=10:4000,
    xlabel = {runtime},
    xmin = 10,
    xmax = 4100,
    ymax = 0,
    ymin = -80000,
    legend to name = ledgendPositionMC,
    legend columns=4,
    width = 0.9\columnwidth,
    scaled ticks = false
    ] 
    \addplot[color=red,mark=x] table[x=time, y=MC-CCFDB-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-old}
    \addplot[color=orange,mark=o] table[x=time, y=MC-CCFDB-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-new}
    \addplot[color=blue,mark=x] table[x=time, y=MC-CCIFD-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-old}
    \addplot[color=cyan,mark=o] table[x=time, y=MC-CCIFD-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-new}
